How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-04-30 tse-paper/content.tex
Make RQ1 fit one line

Despite its central role in helping developers and in enabling
novel, onward processing applications,
the process of how to
%automatically
% ^ we survey manual as well, though leaving it out includes too much
systematically
analyze build logs has thus far not been systematically
overviewed as a research topic, bringing us to the first
research question:
% TODO Discuss: is -research fine? or state-of-the-art more common and
% still not missused (because industry m)
\begin{simplebox}[minipage boxed title*=-5cm]{\textbf{Research Question
1}}
What is the state-of-the-research on analyzing build logs?
\end{simplebox}

@@

This lead us to the following research questions:
\begin{simplebox}[attach boxed title to top center={yshift=-6mm}]
{\textbf{RQ1:} What is the state-of-the-research on analyzing build logs?}
\begin{itemize}[leftmargin=1cm]
  \item[\textbf{RQ1.1:}] What information is targeted in build logs?
  \item[\textbf{RQ1.2:}] Which analysis techniques exist?
  \item[\textbf{RQ1.3:}] Which kinds of build logs are subject to
  analysis?
\end{itemize}
\end{simplebox}

>>>>

Despite its central role in helping developers and in enabling
novel, onward processing applications,
the process of how to
%automatically
% ^ we survey manual as well, though leaving it out includes too much
systematically
analyze build logs has thus far not been systematically
overviewed as a research topic, bringing us to the first
research question:
% TODO Discuss: is -research fine? or state-of-the-art more common and
% still not missused (because industry m)
\begin{simplebox}[minipage boxed title*=-5cm]{\textbf{Research Question
1}}
What is the state-of-research to analyze build logs?
\end{simplebox}

@@

This lead us to the following research questions:
\begin{simplebox}[attach boxed title to top center={yshift=-6mm}]
{\textbf{RQ1:} What is the state-of-research to analyze build logs?}
\begin{itemize}[leftmargin=1cm]
  \item[\textbf{RQ1.1:}] What information is targeted in build logs?
  \item[\textbf{RQ1.2:}] Which analysis techniques exist?
  \item[\textbf{RQ1.3:}] Which kinds of build logs are subject to
  analysis?
\end{itemize}
\end{simplebox}
